Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-01-02 paper.tex
Added description

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/sound_localisation.png}
  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_discrimination.png}
  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds.png}
  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds_limits.png}
  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/target_errors.png}
  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_median_error.png}
  \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
  \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/fitts_ips.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/sound_localisation.png}
  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
  \Description{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_discrimination.png}
  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
  \Description{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds.png}
  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
  \Description{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds_limits.png}
  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
  \Description{Histogram distributions of the participants' 75\% cut-off thresholds. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/target_errors.png}
  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
  \Description{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_median_error.png}
  \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
  \Description{Box-plots of the median pan and elevation errors for each audio setting. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
  \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
  \Description{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
  \Description{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/fitts_ips.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
  \Description{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
\end{figure}
